\chapter{Plotting and Figures}

\section{Introduction}

This chapter will introduce methods for standard TE plotting, flexible plotting recipes.

\section{Fast TE Plotting}

Based on the Raw TE Analysis in Chapter 3, the processed TE data are listed in \code{./data/processed/batch}. The fast plotting can be achieved
by \code{python mian.py plot-te}

\begin{lstlisting}[language=bash, caption={Fast TE plotting.}]
python main.py plot_te BATCH_ID SAMPLE_ID \
  --seebeck --conductivity --power_factor \      
  --xlim LOW HIGH --ylim LOW HIGH \        
  --legend
\end{lstlisting}
The flexible plotting recipes also inclue temperatrue dependent thermoelectric proeprties.
\begin{lstlisting}[language=bash,caption={TE plotting command slot.}]
python main.py flexible \
  --recipe configs/plot_recipes/thermoeletric/temperature_vs_seebeck.json \
  data/demo/thermoelectric_property/1.csv \
\end{lstlisting}

\twofigureslot
  {figures/chapter5/5.1a.pdf}
  {(a) Single batch $S$.}
  {figures/chapter5/5.1b.pdf}
  {(b) Single batch $\kappa_L$.}
  {Fast TE plotting.}

\subsection{TE properties comparison inter batches}
It's important to introduce the methods to plot inter-batches comparision of thermoelectric proeprties. If all data are recorded 
in \code{data\processed} with $batch_id$, the fasted way is to run \code{python plot_te.py}.

\begin{lstlisting}[language=bash, caption={Fast inter-batch TE plotting.}]
python main.py plot_te BATCH_ID_1 BATCH_ID_2 BATCH_ID_3
\end{lstlisting}

Most generally, comparision with references data, to use \code{flexible_plot.py} under different recipes is recomaned.
The data of each sample should have columns with the title used in the program. 
\begin{lstlisting}[language=bash, caption={Plotting multiple reference data.}]
python main.py fleible \      
  --recipe configs/plot_recipes/thermoeletric/temperature_vs_seebeck.json \
  data/demo/thermoelectric_property/{1,2,3,4,5}.csv \      
  --x T --y S \      
  --label 'Sample1' --label '$Cu_{0.2}$' --label '$CU_{0.4}$'\       
  --stem seebeck_comparison
\end{lstlisting}

\twofigureslot
  {figures/chapter5/5.2a.pdf}
  {(a) Single batch $S$.}
  {figures/chapter5/5.2b.pdf}
  {(b) Single batch $\kappa_L$.}
  {Inter batch plotting.}

\section{Planned Content}

\begin{itemize}[leftmargin=*]
  \item Standard single-property and combined TE plots.
  \item Cross-batch comparison figures.
  \item Flexible plotting direct CLI mode versus recipe mode.
  \item Output formats: PNG for quick review, PDF/SVG for manuscripts.
  \item Axis-limit conventions and legend placement.
\end{itemize}/
